Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-11 papers/marlowe2019/paper.tex
Add comma

In the next two sections we give an overview of some of the work we have carried out with the aim of helping users be more confident that the Marlowe contracts they write do what they expect them to do.
We look at two complementary approaches: static analysis of concrete contracts in this section,  and formal verification of general properties about Marlowe in the next.

>>>>

In the next two sections, we give an overview of some of the work we have carried out with the aim of helping users be more confident that the Marlowe contracts they write do what they expect them to do.
We look at two complementary approaches: static analysis of concrete contracts in this section,  and formal verification of general properties about Marlowe in the next.
